%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------

\cventry
{Trainee Developer}
{Platanus}
{Santiago, Chile}
{April. 2021 - June 2021}
{
  \begin{cvitems}
    \item Wrote modular, secure and well tested code in Ruby/Rails and Javascript, currently being used in production.
    \item Partnered with product managers, designers and developers to deeply understand the needs of users, and build value-added features for
    a FinTech product.
  \end{cvitems}
}

\cventry
{Data Scientist at joint venture with Agrosuper S.A. Innovation Group} % Job title
{DICTUC UC} % Organization
{Santiago, Chile} % Location
{March. 2019 - June 2020} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed with full ownership a prototype to detect the presence of risk factors among slaughterhouse workers, using
    machine learning algorithms and inertial sensors to obtain data about their movements.}
    \item {Partnered with stakeholders to understand the problem, improve prototype design, define success metrics and evaluate economic impact.}
    \item {Built a pipeline for ingesting and preparing raw sensor data (ETL), and posterior model training and inference using Python and AWS.}
    \item {Achieved 98\% accuracy in the detection of the two most prevalent risk factors, improving average productivity in 8\%.}
    % \item {Technology stack: Python 3, Scikit-learn, Jupyter Notebook, AWS RDS, AWS EC2, SQLite, Raspberry Pi.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Project Engineer \& Research} % Job title
{Institute for Mathematical and Computational Engineering UC} % Organization
{Santiago, Chile} % Location
{March. 2018 - June 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed APIs for industry clients to forecast future values of critical operational variables using machine learning algorithms.}
    \item {Back-tested the models on historical data, and forecasted the values for three months into the future, reducing average MAPE error to 2\%.}
    % \item {Technology stack: Python 3, Scikit-learn, SQL.}
  \end{cvitems}
}

%---------------------------------------------------------

\cventry
{Chief Teaching Assistant - Big Data for Decision Making Diploma}
{Clase Ejecutiva UC} % Organization
{Santiago, Chile} % Location
{Aug. 2018 - Sept. 2020} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Communicated complex machine learning concepts into useful insights for senior professionals.}
  \end{cvitems}
}

\cventry
{Data Science Internship, Financial Research Group} % Job title
{Central Bank of Chile} % Organization
{Santiago, Chile} % Location
{Dec. 2017 - March. 2018} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Partnered with economists to analyze survey data about debt underreporting in Chilean households, and it's policy implications.}
    \item {Quantified the influence of debt-type and household size in debt underreporting, using regression models in STATA and R.}
  \end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
