%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}

\cvsubsection{Programming \& Data Science}
\begin{cventries}
  \cventry
  {Deep Learning Experiments}
  {}
  {}
  {2019-2020}{
  \begin{cvitems}
   \item { I worked on several DL projects: from image recognition, architecture understanding (CNN, RNN and GANS)
   to NLP tasks (text summarization and text translation). I used Keras and Pytorch.
   The code is available in my GitHub: \url{https://github.com/AdolfoVillalobos/DL_PUC}.}
  \end{cvitems}
   }

  \cventry{Falla UC}{}{}{2019-Present}{
   \begin{cvitems}
   \item  {A web based predictive maintenance dashboard, using AWS Lambda, AWS RDS and
AWS Gateway technologies for the registering and processing of real time temperature sensor data of
machines. I experimented with time series modeling (ARMA, ARIMA, etc.) and
AutoEncoders to detect anomalies. Still on development.}
   \end{cvitems}
}

  \cventry{DebtControl Bots}{}{}{2019-Present}{
  \begin{cvitems}
 \item {A software project focused on the automatization of certain human activities
    related with payment notification. The project was developed for DebtControl,
    a chilean company dedicated to loan servicing. We used Python web-scrapping tools, and
    a raspberry-pi to execute the code.}
  \end{cvitems}
  }
\end{cventries}
\cvsubsection{Extracurricular activites}

\begin{cventries}
  \cventry{Mathematical Academy, Leonardo Murialdo School}
  {}
  {}
  {2013-2015}
  {\begin{cvitems}
    \item {Founder and first teacher of an academy for the training of high school students, to compete in mathematical olympiads.}
  \end{cvitems}
}
  \cventry
  {President, SIAM-PUC Student Chapter}
  {}
  {}
  {Core-Member \& President (2016)}
  {
    \begin{cvitems}
      \item {Reformed the chapter by engaging students to participate in activities focused 
        on understanding the links between pure mathematics and machine learning,
        and encouraged networking between students and professors.}
      \item {Co-organized the National Encounter for Mathematical Engineering 2015, a congress for undergraduate students interested in applied mathematics.}
    \end{cvitems}
    }
\end{cventries}

 

